---
title: 'Reproducible report: Incidence-severity relationships in unmanaged and fungicide-protected wheat head blast epidemics in Brazil'
output:
  html_document:
    css: style.css
    depth: 5
    number_sections: no
    theme: default
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
date: 'Created: 2021-10-06 <br/>Last update: `r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages 
```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(ggplot2)
library(metafor)
library(car)
library(ggthemes)
library(cowplot)
library(scales)
library(dplyr)
library(readxl)
library(lme4)
library(lmerTest)
library(report)
library(patchwork)
library(merTools)
library(ciTools)
library(parameters)
library(performance)
library(see)
library(data.table)

```
 

# Importing data 

```{r}

data_epamig <- read_excel("Data/data_epamig.xlsx")
general_slim_data <- read_excel("Data/generalslim_data.xlsx")


```


```{r}

general_slim_data %>%
  ggplot(aes(inc_mean, index_mean))+
  geom_point()+
  geom_smooth()+
  facet_wrap( ~ source)

```



# Summary and data transformation 

```{r}

epamig_data <- data_epamig %>% 
  mutate(idx = (inc*dhs)/100) %>% 
  relocate(idx, .before = tgw) %>% 
  mutate(clog_inc = log(-log(1 - (inc/100))),
         clog_idx = log(-log(1 - (idx/100)))) %>% 
  dplyr::filter(idx > 0) %>% 
  dplyr::filter(!cultivar == "SINTONIA")

rede_data <- general_slim_data %>% 
  dplyr::filter(source == "REC-Embrapa") %>% 
  dplyr::filter(index_mean > 0) %>% 
  mutate(inc_rede = case_when(inc_mean == 100 ~ 99,
                              inc_mean <= 99.9 ~ inc_mean),
         idx_rede = case_when(index_mean == 100 ~ 99,
                              index_mean <= 99.9 ~ index_mean)) %>% 
  mutate(clog_inc = log(-log(1 - (inc_rede/100))),
         clog_idx = log(-log(1 - (idx_rede/100))))
  

```

# Interactions 
```{r}

aa <- lm(clog_idx ~ clog_inc*year, data = epamig_data)
bb <- lm(clog_idx ~ clog_inc*cultivar, data = epamig_data)

anova(aa)
anova(bb)


```


# Separating the EPAMIG data for each year

```{r}

data_2013 <- epamig_data %>% 
  filter(year == 2013)

data_2014 <- epamig_data %>% 
  filter(year == 2014)

data_2015 <- epamig_data %>% 
  filter(year == 2015)

data_2016 <- epamig_data %>% 
  filter(year == 2016)

data_2017 <- epamig_data %>% 
  filter(year == 2017)

data_2018 <- epamig_data %>% 
  filter(year == 2018)

data_2019 <- epamig_data %>% 
  filter(year == 2019)
```

# Linear Regression model 

## UFTs data
```{r}
lm_pooled_rede <- lm(clog_idx ~ clog_inc, data = rede_data)
summary(lm_pooled_rede)
report(lm_pooled_rede)
anova(lm_pooled_rede)
car::linearHypothesis(lm_pooled_rede, "clog_inc = 1")
```

## EPAMIG pooled data 
```{r}
lm_pooled <- lm(clog_idx ~ clog_inc, data = epamig_data)
summary(lm_pooled)
report(lm_pooled)
anova(lm_pooled)
car::linearHypothesis(lm_pooled, "clog_inc = 1")
```

## 2013
```{r}
lm_2013 <- lm(clog_idx ~ clog_inc, data = data_2013)
summary(lm_2013)
report(lm_2013)
anova(lm_2013)
car::linearHypothesis(lm_2013, "clog_inc = 1")
```

## 2014
```{r}
lm_2014 <- lm(clog_idx ~ clog_inc, data = data_2014)
summary(lm_2014)
anova(lm_2014)
report(lm_2014)
car::linearHypothesis(lm_2014, "clog_inc = 1")
```

## 2015
```{r}
lm_2015 <- lm(clog_idx ~ clog_inc, data = data_2015)
summary(lm_2015)
anova(lm_2015)
report(lm_2015)
car::linearHypothesis(lm_2015, "clog_inc = 1")
```

## 2016
```{r}
lm_2016 <- lm(clog_idx ~ clog_inc, data = data_2016)
summary(lm_2016)
anova(lm_2016)
report(lm_2016)
car::linearHypothesis(lm_2016, "clog_inc = 1")
```

## EPAMIG 2017
```{r}
lm_2017 <- lm(clog_idx ~ clog_inc, data = data_2017)
summary(lm_2017)
anova(lm_2017)
report(lm_2017)
car::linearHypothesis(lm_2017, "clog_inc = 1")
```

## EPAMIG 2018
```{r}
lm_2018 <- lm(clog_idx ~ clog_inc, data = data_2018)
summary(lm_2018)
anova(lm_2018)
report(lm_2018)
car::linearHypothesis(lm_2018, "clog_inc = 1")
```

## EPAMIG 2019
```{r}
lm_2019 <- lm(clog_idx ~ clog_inc, data = data_2019)
summary(lm_2019)
anova(lm_2019)
report(lm_2019)
car::linearHypothesis(lm_2019, "clog_inc = 1")
```

# Predition interval 
## 2013
```{r}

predict_lm_2013 <- predict(lm_2013, data_2013, se.fit = TRUE,
                           interval = "prediction")

a.13 <- data.frame(predict_lm_2013) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2013 <- cbind(data_2013,a.13)


```

## 2014
```{r}
predict_lm_2014 <- predict(lm_2014, data_2014, se.fit = TRUE,
                           interval = "prediction")

a.14 <- data.frame(predict_lm_2014) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2014 <- cbind(data_2014,a.14)

```

## 2015
```{r}
predict_lm_2015 <- predict(lm_2015, data_2015, se.fit = TRUE,
                           interval = "prediction")

a.15 <- data.frame(predict_lm_2015) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2015 <- cbind(data_2015,a.15)
```

## 2016
```{r}
predict_lm_2016 <- predict(lm_2016, data_2016, se.fit = TRUE,
                           interval = "prediction")

a.16 <- data.frame(predict_lm_2016) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2016 <- cbind(data_2016,a.16)
```

## 2017
```{r}
predict_lm_2017 <- predict(lm_2017, data_2017, se.fit = TRUE,
                           interval = "prediction")

a.17 <- data.frame(predict_lm_2017) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2017 <- cbind(data_2017,a.17)
```

## 2018
```{r}
predict_lm_2018 <- predict(lm_2018, data_2018, se.fit = TRUE,
                           interval = "prediction")

a.18 <- data.frame(predict_lm_2018) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2018 <- cbind(data_2018,a.18)
```

## 2019
```{r}
predict_lm_2019 <- predict(lm_2019, data_2019, se.fit = TRUE,
                           interval = "prediction")

a.19 <- data.frame(predict_lm_2019) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

data_2019 <- cbind(data_2019,a.19)
```

## EPAMIG Pooled data
```{r}
predict_lm_pooled <- predict(lm_pooled, epamig_data, se.fit = TRUE,
                           interval = "prediction")

a.pooled <- data.frame(predict_lm_pooled) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

epamig_data <- cbind(epamig_data,a.pooled)
```
## UFTs data

```{r}
predict_lm_pooled_rede <- predict(lm_pooled_rede, rede_data, se.fit = TRUE,
                           interval = "prediction")

a.pooled_rede <- data.frame(predict_lm_pooled_rede) %>% 
  rownames_to_column(var = "ID") %>% 
  dplyr::select(-c(6,7))

rede_data <- cbind(rede_data,a.pooled_rede)


```


# MSE
```{r}
S_2013 <- summary(lm_2013)
MSE_2013 <- mean(S_2013$residuals^2)

S_2014 <- summary(lm_2014)
MSE_2014 <- mean(S_2014$residuals^2)

S_2015 <- summary(lm_2015)
MSE_2015 <- mean(S_2015$residuals^2)

S_2016 <- summary(lm_2016)
MSE_2016 <- mean(S_2016$residuals^2)

S_2017 <- summary(lm_2017)
MSE_2017 <- mean(S_2017$residuals^2)

S_2018 <- summary(lm_2018)
MSE_2018 <- mean(S_2018$residuals^2)

S_2019 <- summary(lm_2019)
MSE_2019 <- mean(S_2019$residuals^2)

S_pool <- summary(lm_pooled)
MSE_pool <- mean(S_pool$residuals^2)

S_pool_rede <- summary(lm_pooled_rede)
MSE_pool_rede <- mean(S_pool_rede$residual^2)
```


# V
## 2013 
```{r}
se_b0_2013<- S_2013$coefficients[3]
V_b0_2013 <- MSE_2013 + se_b0_2013^2
```
## 2014
```{r}
se_b0_2014 <- S_2014$coefficients[3]
V_b0_2014 <- MSE_2014 + se_b0_2014^2
```
## 2015
```{r}
se_b0_2015 <- S_2015$coefficients[3]
V_b0_2015 <- MSE_2015 + se_b0_2015^2
```
## 2016
```{r}
se_b0_2016 <- S_2016$coefficients[3]
V_b0_2016 <- MSE_2016 + se_b0_2016^2
```
## 2017
```{r}
se_b0_2017 <- S_2017$coefficients[3]
V_b0_2017 <- MSE_2017 + se_b0_2017^2
```
## 2018
```{r}
se_b0_2018 <- S_2018$coefficients[3]
V_b0_2018 <- MSE_2018 + se_b0_2018^2
```
## 2019
```{r}
se_b0_2019 <- S_2019$coefficients[3]
V_b0_2019 <- MSE_2019 + se_b0_2019^2
```
## EPAMIG pooled data
```{r}
se_b0_pooled <- S_pool$coefficients[3]
V_b0_pooled <- MSE_pool + se_b0_pooled^2
```
## UFTs data
```{r}
se_b0_pooled_rede <- S_pool_rede$coefficients[3]
V_b0_pooled_rede <- MSE_pool_rede + se_b0_pooled_rede^2
```


# Correlation between predicted severity and actual values 
## 2013
```{r}

predict_lm_2013 <- predict(lm_2013, data_2013, type = "response")

plot(data_2013$clog_idx, predict_lm_2013)

cor(data_2013$clog_idx, predict_lm_2013)^2

```

## 2014
```{r}
predict_lm_2014 <- predict(lm_2014, data_2014, type = "response")

plot(data_2014$clog_idx, predict_lm_2014)

cor(data_2014$clog_idx, predict_lm_2014)^2
```

## 2015
```{r}
predict_lm_2015 <- predict(lm_2015, data_2015, type = "response")

plot(data_2015$clog_idx, predict_lm_2015)

cor(data_2015$clog_idx, predict_lm_2015)^2
```

## 2016
```{r}
predict_lm_2016 <- predict(lm_2016, data_2016, type = "response")

plot(data_2016$clog_idx, predict_lm_2016)

cor(data_2016$clog_idx, predict_lm_2016)^2
```

## 2017
```{r}
predict_lm_2017 <- predict(lm_2017, data_2017, type = "response")

plot(data_2017$clog_idx, predict_lm_2017)

cor(data_2017$clog_idx, predict_lm_2017)^2
```

## 2018
```{r}
predict_lm_2018 <- predict(lm_2018, data_2018, type = "response")

plot(data_2018$clog_idx, predict_lm_2018)

cor(data_2018$clog_idx, predict_lm_2018)^2
```

## 2019
```{r}
predict_lm_2019 <- predict(lm_2019, data_2019, type = "response")

plot(data_2019$clog_idx, predict_lm_2019)

cor(data_2019$clog_idx, predict_lm_2019)^2
```

## EPAMIG pooled data
```{r}
predict_lm_pooled <- predict(lm_pooled, epamig_data, type = "response")

plot(epamig_data$clog_idx, predict_lm_pooled)

cor(epamig_data$clog_idx, predict_lm_pooled)^2
```

## UFTs data 

```{r}
predict_lm_pooled_rede <- predict(lm_pooled_rede, rede_data, type = "response")

plot(rede_data$clog_idx, predict_lm_pooled_rede)

cor(rede_data$clog_idx, predict_lm_pooled_rede)^2
```


# Prediciton of INC

## Extraction of Lm coefficients
```{r}
b0_2013 <- lm_2013$coefficients[1]
b1_2013 <- lm_2013$coefficients[2]

b0_2014 <- lm_2014$coefficients[1]
b1_2014 <- lm_2014$coefficients[2]

b0_2015 <- lm_2015$coefficients[1]
b1_2015 <- lm_2015$coefficients[2]

b0_2016 <- lm_2016$coefficients[1]
b1_2016 <- lm_2016$coefficients[2]

b0_2017 <- lm_2017$coefficients[1]
b1_2017 <- lm_2017$coefficients[2]

b0_2018 <- lm_2018$coefficients[1]
b1_2018 <- lm_2018$coefficients[2]

b0_2019 <- lm_2019$coefficients[1]
b1_2019 <- lm_2019$coefficients[2]

b0_pooled <- lm_pooled$coefficients[1]
b1_pooled <- lm_pooled$coefficients[2]

b0_pooled_rede <- lm_pooled_rede$coefficients[1]
b1_pooled_rede <- lm_pooled_rede$coefficients[2]
```

## Prediction of the incidence from a known severity (10%)
```{r}
# complementary log-log transformation function
CLL = function(X){
  log(-log(1 - X))
}


idx10 <- CLL(0.1)

inc_10_2013 <- 1 - exp( -exp((idx10 - b0_2013)/b1_2013)) 

inc_10_2014 <- 1 - exp( -exp((idx10 - b0_2014)/b1_2014))

inc_10_2015 <- 1 - exp( -exp((idx10 - b0_2015)/b1_2015))

inc_10_2016 <- 1 - exp( -exp((idx10 - b0_2016)/b1_2016))

inc_10_2017 <- 1 - exp( -exp((idx10 - b0_2017)/b1_2017))

inc_10_2018 <- 1 - exp( -exp((idx10 - b0_2018)/b1_2018))

inc_10_2019 <- 1 - exp( -exp((idx10 - b0_2019)/b1_2019))

inc_10_pooled <- 1 - exp( -exp((idx10 - b0_pooled)/b1_pooled))

inc_10_pooled_rede <- 1 - exp( -exp((idx10 - b0_pooled_rede)/b1_pooled_rede))
```

## Prediction of the severity from incidence

```{r}
sev_2013 <- 1 - exp(-exp(b0_2013 + (b1_2013 * CLL(0.2))))

sev_2014 <- 1 - exp(-exp(b0_2014 + (b1_2014 * CLL(0.2))))

sev_2015 <- 1 - exp(-exp(b0_2015 + (b1_2015 * CLL(0.2))))

sev_2016 <- 1 - exp(-exp(b0_2016 + (b1_2016 * CLL(0.2))))

sev_2017 <- 1 - exp(-exp(b0_2017 + (b1_2017 * CLL(0.2))))

sev_2018 <- 1 - exp(-exp(b0_2018 + (b1_2018 * CLL(0.2))))

sev_2019 <- 1 - exp(-exp(b0_2019 + (b1_2019 * CLL(0.2))))

sev_pooled <- 1 - exp(-exp(b0_pooled + (b1_pooled * CLL(0.2))))

sev_pooled_rede <- 1 - exp(-exp(b0_pooled_rede + (b1_pooled_rede * CLL(0.2))))
```


# Graphics 

## Boxplot EPAMIG
```{r}
box01 <- epamig_data %>% 
  ggplot(aes(as.factor(year),(inc/100)))+ 
  # geom_jitter(width = 0.2,
              # size = 1.3,
              # alpha = 0.3)+
  geom_boxplot(alpha = 0.2,
               outlier.shape = NA, 
               size = 0.9,
               width = 0.7)+
  scale_color_colorblind()+
  scale_fill_colorblind()+
  theme_half_open()+
  xlab("EPAMIG")+
  ylab("Incidence")+
  theme(legend.position = "top")+
  labs(color = "Cultivar", fill = "Cultivar")


box02 <- epamig_data %>% 
  ggplot(aes(as.factor(year),(idx/100)))+ 
  # geom_jitter(width = 0.2,
              # size = 1.3,
              # alpha = 0.3)+
  geom_boxplot(alpha = 0.2,
               outlier.shape = NA, 
               size = 0.9,
               width = 0.7)+
  scale_color_colorblind()+
  scale_fill_colorblind()+
  theme_half_open()+
  xlab("EPAMIG")+
  ylab("Severity")+
  theme(legend.position = "top")+
  labs(color = "Cultivar",
       fill = "Cultivar")
       


```

## Boxplot UFTs 

```{r}
box03 <- rede_data %>% 
  mutate(graf = "UFTs") %>% 
  ggplot(aes(graf, (inc_rede/100))) + 
  geom_boxplot(alpha = 0.2,
               outlier.shape = NA, 
               size = 0.9,
               width = 0.3)+
  scale_color_colorblind()+
  scale_fill_colorblind()+
  theme_half_open()+
  xlab("UFTs")+
  ylab("")+
  theme(legend.position = "top",
        axis.text.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank())
  
box04 <- rede_data %>% 
  mutate(graf = "UFTs") %>% 
  ggplot(aes(graf, (idx_rede/100))) + 
  geom_boxplot(alpha = 0.2,
               outlier.shape = NA, 
               size = 0.9,
               width = 0.3)+
  scale_color_colorblind()+
  scale_fill_colorblind()+
  theme_half_open()+
  xlab("UFTs")+
  ylab("")+
  theme(legend.position = "top",
        axis.text.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank())
  



```


## Histograms 

```{r}

hist01 <- epamig_data %>% 
  ggplot(aes(inc))+
  geom_histogram(color = "black",
                 fill = "black",
                 alpha = 0.1)+
  geom_vline(xintercept = 35.70,
             size = 1.2,
             linetype = 2)+
  ylab("")+
  xlab("I (%)")+
  theme_minimal_hgrid()

```

```{r}
hist02 <- epamig_data %>% 
  ggplot(aes(dhs))+
  geom_histogram(color = "black",
                 fill = "black",
                 alpha = 0.1)+
  geom_vline(xintercept = 53.04,
             size = 1.2,
             linetype = 2)+
  ylab("")+
  xlab("DHS (%)")+
  theme_minimal_hgrid()

```

```{r}
hist03 <- epamig_data %>% 
  ggplot(aes(idx))+
  geom_histogram(color = "black",
                 fill = "black",
                 alpha = 0.1)+
  geom_vline(xintercept = 22.60,
             size = 1.2,
             linetype = 2)+
  ylab("")+
  xlab("S (%)")+
  theme_minimal_hgrid()
```

```{r}

hist01_rede <- rede_data %>% 
  ggplot(aes(inc_rede))+
  geom_histogram(color = "black",
                 fill = "black",
                 alpha = 0.1)+
  geom_vline(xintercept = 41.85,
             size = 1.2,
             linetype = 2)+
  ylab("")+
  xlab("I (%)")+
  theme_minimal_hgrid()

```

```{r}

hist02_rede <- rede_data %>% 
  ggplot(aes(sev_mean))+
  geom_histogram(color = "black",
                 fill = "black",
                 alpha = 0.1)+
  geom_vline(xintercept = 31.75,
             size = 1.2,
             linetype = 2)+
  ylab("")+
  xlab("DHS (%)")+
  theme_minimal_hgrid()

```

```{r}
hist03_rede <- rede_data %>% 
  ggplot(aes(idx_rede))+
  geom_histogram(color = "black",
                 fill = "black",
                 alpha = 0.1)+
  geom_vline(xintercept = 22.9,
             size = 1.2,
             linetype = 2)+
  ylab("")+
  xlab("S (%)")+
  theme_minimal_hgrid()
```


## Patchwork of histograms and boxplots 

```{r message=FALSE, warning=FALSE}
layout <- "
AABBCC
DDEEFF
GGGGHH
IIIIJJ
"
hist01 + hist02 + hist03 + hist01_rede + hist02_rede + hist03_rede + box01 + box03 + box02 + box04 +
  plot_layout(design = layout)+
  plot_annotation(tag_levels = 'A')

ggsave("figures/boxplot_histo.png", width = 6, height = 9)
```


## Regression graphics (CLL) and back-transformad data

### 2013 CLL

```{r warning=FALSE}

GCLL_2013 <- data_2013 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2013, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2013, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2013, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2013)+
  ylab("CLL Severity ")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()


```


### 2013 Back-transformation 


```{r warning=FALSE}

GB_2013 <- data_2013 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2013, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2013, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2013, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2013)+
  coord_fixed()+
  theme_half_open()


```

### 2014 CLL

```{r warning=FALSE}

GCLL_2014 <- data_2014 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2014, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2014, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2014, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2014)+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()
  

```


### 2014 Back-transformed data

```{r warning=FALSE}

GB_2014 <- data_2014 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2014, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2014, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2014, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2014)+
  coord_fixed()+
  theme_half_open()

```


### 2015 CLL

```{r warning=FALSE}



GCLL_2015 <- data_2015 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2015, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2015, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2015, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2015)+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()
  
  


```

### 2015 Back-trasformed 

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1) 

# incidx_2015 <- (b0_2015 + (b1_2015*seq01))

# graf_2015 <- data.frame(incidx_2015) 



GB_2015 <- data_2015 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2015, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2015, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2015, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2015)+
  coord_fixed()+
  theme_half_open()



```


### 2016 CLL

```{r warning=FALSE}



GCLL_2016 <- data_2016 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2016, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2016, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2016, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2016)+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()


```

### 2016 Back-transformed

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1) 

# incidx_2016 <- (b0_2016 + (b1_2016*seq01))

# graf_2016 <- data.frame(incidx_2016) 



GB_2016 <- data_2016 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2016, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2016, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2016, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2016)+
  coord_fixed()+
  theme_half_open()

```

### 2017 CLL

```{r warning=FALSE}



GCLL_2017 <- data_2017 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2017, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2017, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2017, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2017)+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()

```

### 2017 back-transformed

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1) 

# incidx_2017 <- (b0_2017 + (b1_2017*seq01))

# graf_2017 <- data.frame(incidx_2017) 



GB_2017 <- data_2017 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2017, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2017, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2017, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2017)+
  coord_fixed()+
  theme_half_open()

```


### 2018 CLL

```{r warning=FALSE}



GCLL_2018 <- data_2018 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2018, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2018, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2018, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2018)+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()

```

### 2018 Back-transformed

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1) 

# incidx_2018 <- (b0_2018 + (b1_2018*seq01))

# graf_2018 <- data.frame(incidx_2018) 


GB_2018 = data_2018 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2018, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2018, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2018, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2018)+
  coord_fixed()+
  theme_half_open()

```


### 2019 CLL

```{r warning=FALSE}


GCLL_2019 = data_2019 %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2019, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = data_2019, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = data_2019, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = 2019)+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()

```

### 2019 Back-transformed

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1) 

# incidx_2019 <- (b0_2019 + (b1_2019*seq01))

# graf_2019 <- data.frame(incidx_2019) 


GB_2019 = data_2019 %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.5,
             width = 0.5)+
  geom_line(data = data_2019, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = data_2019, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = data_2019, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = 2019)+
  coord_fixed()+
  theme_half_open()
```

### Pooled CLL

```{r warning=FALSE}


GCLL_pool <- epamig_data %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.1,
             width = 0.5)+
  geom_line(data = epamig_data, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = epamig_data, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = epamig_data, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = "EPAMIG")+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()

```


### Pooled Back-transformed

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1) 

# incidx_pooled <- (b0_pooled + (b1_pooled*seq01))

# graf_pooled <- data.frame(incidx_pooled) 



GB_pool <- epamig_data %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.1,
             width = 0.5)+
  geom_line(data = epamig_data, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = epamig_data, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = epamig_data, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = "EPAMIG")+
  coord_fixed()+
  theme_half_open()

```

### Pooled rede

```{r warning=FALSE}
GCLL_pool_rede <- rede_data %>% 
  ggplot(aes(clog_inc, clog_idx))+
  geom_point(size = 2, 
             color = "black",
             alpha = 0.1,
             width = 0.5)+
  geom_line(data = rede_data, aes(clog_inc, fit.fit),
            size = 1.2)+
  geom_line(data = rede_data, aes(clog_inc, fit.lwr),
            linetype = 2,
            size = 0.5)+
  geom_line(data = rede_data, aes(clog_inc, fit.upr),
            linetype = 2,
            size = 0.5)+
  xlim(-6,1)+
  ylim(-6,1)+
  labs(title = "UFTs")+
  ylab("CLL Severity")+
  xlab("CLL Incidence")+
  coord_fixed()+
  # ylim(-6, 2)+
  theme_half_open()

```


### Pooled Rede Back-transformed

```{r warning=FALSE}

# seq01 <- seq(-4.60, cem, by = 0.1)

# incidx_pooled <- (b0_pooled + (b1_pooled*seq01))

# graf_pooled <- data.frame(incidx_pooled) 



GB_pool_rede <- rede_data %>% 
  ggplot(aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(clog_idx)))))+
  geom_point(color = "black",
             size = 2,
             alpha = 0.1,
             width = 0.5)+
  geom_line(data = rede_data, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.fit)))),
            size = 1.5)+
  geom_line(data = rede_data, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.lwr)))),
            size = 0.5,
            linetype = 2)+
  geom_line(data = rede_data, aes((1 - exp(-exp(clog_inc))), (1 - exp(-exp(fit.upr)))),
            size = 0.5,
            linetype = 2)+
  ylab("Severity")+
  xlab("Incidence")+
  xlim(0,1)+
  ylim(0,1)+
  labs(title = "UFTs")+
  coord_fixed()+
  theme_half_open()

```

GCLL_2013 GB_2013
## Patchwork
### CLL
```{r message=FALSE, warning=FALSE}

(GCLL_2013 + GCLL_2014 + GCLL_2015 + GCLL_2016 + GCLL_2017 + GCLL_2018 + GCLL_2019)+ 
  plot_layout(ncol = 2)

ggsave("figures/CLLplots02.png", width = 13, height = 15)


```


### Back-transformed

```{r message=FALSE, warning=FALSE}

(GB_2013 + GB_2014 + GB_2015 + GB_2016 + GB_2017 + GB_2018 + GB_2019)+ 
  plot_layout(ncol = 2)
  
ggsave("figures/BTplots02.png", width = 13, height = 15)

```


### Pooleds

```{r message=FALSE, warning=FALSE}
(GCLL_pool + GCLL_pool_rede +  GB_pool +  GB_pool_rede)+ 
  plot_layout(ncol = 2)
  
ggsave("figures/Pooleds.png", width = 7, height = 7)


```











